The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-03-12 response.txt

Comment on styles:
As it was not related to the section, we removed the first paragraph 
in the APE section that commented on different styles.  However, we
did add a comment in the affiliated package section indicating that
they may have different requirements and structure than the core package.

Comment on NDData:
At the time of initial development, the developers were not aware of 
any open source packages that would have fit the requirements of NDData.  Since
then, we have been working with different groups (LSST, sunpy) to coordinate
development of the NDData interface as well as assessing other attempts at 
something similar.  There is currently an APE about this under 
discussion (https://github.com/astropy/astropy-APEs/pull/14)  .

> More generally, given the technical nature of the work being described here,
> I frequently found myself wanting a small code snippet that demonstrated the
> new/improved functionality of the packages being described. Perhaps the
> authors could find a way to include short code examples where appropriate,
> either inline in the paper body or in the appendix.

We did include code snippets in the first astropy paper from 2013. 
However, we have made a conscious decision to avoid that this time 
due to the following reasons:

@@

- Most new features would require some setup. For example, showing the
  code for WCS axis plotting is not very useful without loading an
  image with a WCS in it first. More complex features profit more from
  code examples, but they also require much more setup to make such an
  example self-consistent and useful. Again, the documentation is a better
  place for that.

As a compromise, we have added links to the documentation in many places and
there is a link in the introduction that points to the github repository where
this article is written. That repository contains (and the text in the
introduction says this) the scripts that we used to generate the figures.

> Specific issues that need to be corrected: There are some errors in the paper
> (inline comments left where appropriate), for example, Figure 6 has a fairly
> major issue with either the wrong caption or the wrong figure but I'm sure
> this is easily addressed. I have left comments throughout the modified
> 'main.tex' file in the form `\inlinecomment{REVIEWER}{Comment}`

We have updated Figure 6 to have the correct caption. Inline comments
were also addressed throughout the text.

### 2018-03-12 author.tex
Update author.tex
fixed missing parentheses
Minor wording changes
added an additional author

\newcommand{\afprinceton}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
\newcommand{\afstsci}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
\newcommand{\afsaao}{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
\newcommand{\afminnstate}{Department of Physics and Astronomy, Minnesota State University Moorhead, 1104 7th Ave S, Moorhead, MN 56563}
\newcommand{\afgoddard}{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
\newcommand{\afcfa}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
\newcommand{\afwesternontario}{Department of Physics \& Astronomy, University of Western Ontario, 1151 Richmond St, London ON N5X4H1 Canada}
\newcommand{\afnasaames}{NASA Ames Research Center, Moffett Field, CA 94043, USA}
\newcommand{\afjhu}{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
\newcommand{\afmpik}{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
\newcommand{\afioa}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}
\newcommand{\afpennstate}{Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}
\newcommand{\afgemini}{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
\newcommand{\aflco}{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA}
\newcommand{\afucsb}{Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
\newcommand{\afesomunich}{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}
\newcommand{\afuw}{Department of Astronomy, University of Washington, Seattle, WA 98155}
\newcommand{\afberkeleyastro}{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA}
\newcommand{\afuct}{Department of Astronomy, University of Cape Town, Private Bag X3, Rondebosch 7701, South Africa}

@@

@@

\author{P. Hirst}
\affiliation{\afgemini}

@@

\author{M. Mueller}
\affil{Brown University/Department of Mathematics, 151 Thayer Street, Providence, RI 02912, USA}

@@

\author[0000-0002-5445-5401]{G. R. Tremblay}
\affiliation{{\afcfa}

\author{J. E. H. Turner}
\affiliation{\afgemini}

>>>>

\newcommand{\afprinceton}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
\newcommand{\afstsci}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
\newcommand{\afsaao}{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
\newcommand{\afminnstate}{Department of Physics and Astronomy, Minnesota State University Moorhead, 1104 7th Ave S, Moorhead, MN 56563}
\newcommand{\afgoddard}{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
\newcommand{\afcfa}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
\newcommand{\afwesternontario}{Department of Physics \& Astronomy, University of Western Ontario, 1151 Richmond St, London ON N5X4H1 Canada}
\newcommand{\afnasaames}{NASA Ames Research Center, Moffett Field, CA 94043, USA}
\newcommand{\afjhu}{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
\newcommand{\afmpik}{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
\newcommand{\afioa}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}
\newcommand{\afpennstate}{Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}
\newcommand{\afgeminin}{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
\newcommand{\afgeminis}{Gemini Observatory, Casilla 603, La Serena, Chile}
\newcommand{\aflco}{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA}
\newcommand{\afucsb}{Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
\newcommand{\afesomunich}{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}
\newcommand{\afuw}{Department of Astronomy, University of Washington, Seattle, WA 98155}
\newcommand{\afberkeleyastro}{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA}
\newcommand{\afuct}{Department of Astronomy, University of Cape Town, Private Bag X3, Rondebosch 7701, South Africa}

@@

\author[0000-0002-2618-1124]{Y. P. Bach}
\affiliation{Department of Physics and Astronomy, Seoul National University, Gwanak-gu, Seoul 08826, South Korea}

@@

\author{P. Hirst}
\affiliation{\afgeminin}

@@

\author{M. Mueller}
\affil{Department of Mathematics, Brown University, 151 Thayer Street, Providence, RI 02912, USA}

@@

\author[0000-0002-5445-5401]{G. R. Tremblay}
\affiliation{{\afcfa}}

\author{J. E. H. Turner}
\affiliation{\afgeminis}

### 2018-03-12 main.tex
small update to figure caption
added an additional author

\begin{figure}
\includegraphics[width=\textwidth]{ngc6977}
\caption{An RGB color image of the region near the Hickson 88 group
constructed from SDSS images and the \astropysubpkg{visualization}
tools.
This example uses \astropywcsaxes to display the
sky coordinate grid, and the
\href{http://docs.astropy.org/en/stable/api/astropy.visualization.make_lupton_rgb.html}{\texttt{make\_lupton\_rgb()}}
function to produce the RGB image from three SDSS filter images ($g$, $r$, $i$).
\label{fig:ngc6977}}
\end{figure}

@@

The following individuals would like to recognize support for their personal contributions.
HMG was supported by the National Aeronautics and Space Administration through the
Smithsonian Astrophysical Observatory contract SV3-73016 to MIT for Support of the Chandra X-Ray Center, which is
operated by the Smithsonian Astrophysical Observatory for and on behalf of the National Aeronautics Space
Administration under contract NAS8-03060. JTV was supported by the UW eScience Institute, via grants from the Moore
Foundation, the Sloan Foundation, and the Washington Research Foundation. SMC acknowledges the National Research
Foundation of South Africa. TLA was supported by NASA contract NAS8-03060. Support for EJT. was provided by NASA
through Hubble Fellowship grant No. 51316.01 awarded by the Space Telescope Science Institute, which is operated by
the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555, as well as a
Giacconi Fellowship. MB was supported by the FONDECYT regular project 1170618 and the MINEDUC-UA projects codes
ANT 1655 and ANT 1656. DH was supported through the SFB 881 ``The Milky Way System'' by the German Research Foundation
(DFG). WEK was supported by an ESO Fellowship. C.M. is supported by NSF grant AST-1313484. SP was supported by
grant AYA2016-75808-R (FEDER) issued by the Spanish government. JEHT was supported by the Gemini Observatory, which
is operated by the Association of Universities for Research in Astronomy, Inc., on behalf of the international
Gemini partnership of Argentina, Brazil, Canada, Chile, and the United States of America.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{ngc6977}
\caption{An RGB color image of the region near the Hickson 88 group
constructed from SDSS images and the \astropysubpkg{visualization}
tools.
This example uses \astropywcsaxes to display the
sky coordinate grid, and the
\href{http://docs.astropy.org/en/stable/api/astropy.visualization.make_lupton_rgb.html}{\texttt{make\_lupton\_rgb()}}
function to produce the RGB image from three SDSS filter images ($g$, $r$, $i$).  The image  on the left shows 
the image with the default parameters, whereas the image on the right has paramets set to show a greater dynamical range. 
\label{fig:ngc6977}}
\end{figure}

@@

The following individuals would like to recognize support for their personal contributions.
HMG was supported by the National Aeronautics and Space Administration through the
Smithsonian Astrophysical Observatory contract SV3-73016 to MIT for Support of the Chandra X-Ray Center, which is
operated by the Smithsonian Astrophysical Observatory for and on behalf of the National Aeronautics Space
Administration under contract NAS8-03060. JTV was supported by the UW eScience Institute, via grants from the Moore
Foundation, the Sloan Foundation, and the Washington Research Foundation. SMC acknowledges the National Research
Foundation of South Africa. TLA was supported by NASA contract NAS8-03060. Support for EJT. was provided by NASA
through Hubble Fellowship grant No. 51316.01 awarded by the Space Telescope Science Institute, which is operated by
the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555, as well as a
Giacconi Fellowship. MB was supported by the FONDECYT regular project 1170618 and the MINEDUC-UA projects codes
ANT 1655 and ANT 1656. DH was supported through the SFB 881 ``The Milky Way System'' by the German Research Foundation
(DFG). WEK was supported by an ESO Fellowship. C.M. is supported by NSF grant AST-1313484. SP was supported by
grant AYA2016-75808-R (FEDER) issued by the Spanish government. JEHT was supported by the Gemini Observatory, which
is operated by the Association of Universities for Research in Astronomy, Inc., on behalf of the international
Gemini partnership of Argentina, Brazil, Canada, Chile, and the United States of America.  YPB was supported by 
the Korea Astronomy and Space Science Institute under the R\&D program supervised by the Ministry of Science, 
ICT and Future Planning.
